Predicting Covid Data

### 2022-12-05 main.rmd

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
- They then use the function to approximate the number of cumulative positive cases in Italy
- Then performed 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
- This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

## Ciufolini and Paolozzi's Study

@@

- add more...

@@

## Works Cited
- Link to study:
- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to covid data:
- https://covid19.who.int/

>>>>

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
- They then use the function to approximate the number of cumulative positive cases in Italy
- Then performed 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
- This study does not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc. 
=======
## The Monte Carlo Study:

**Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations**

<br>

*Author: Ignazio Ciufolini, Antonio Paolozzi*

## Introduction : Ciufolini and Paolozzi's Study

* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
  * They have then use the function to approximate the number of cumulative positive cases in Italy
  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

## Cont.

@@

* create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
- add more...

@@

## Works Cited
- Link to study:
- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to covid data:
- https://covid19.who.int/
- source to find the second derivative of fitted function:
- https://proofwiki.org/wiki/Derivative_of_Error_Function
